---
title: "DKFZ - SMART-CARE interview - coding task"
author: Siwen Chen
date: "`r Sys.Date()`"
theme: united
highlight: tango
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float:
      collapsed: true
      smooth_scroll: false
tags: protein_abundance
---
# Packages used in this workflow
```{r used_packages}
library(DEP)
```

# Data Loading - Raw protein abundance data
```{r protein_abundance_data}
prot_abundance <- read.table(file = "Protein_abundance.tsv",
                              sep = "\t", header = TRUE)
head(prot_abundance, 2)
```

Give the dimension of the protein abundance data - containing 3941 proteins and 49 samples.
```{r}
dim(prot_abundance)
```

Check if there is any duplicated proteins - no duplicated protein.
```{r}
anyDuplicated(prot_abundance$X1)
```


#### Data Size - how many patients, how many proteins

### annotation data
```{r annotation}
## Loading required package: readxl
# annotation <- read_excel("sampleAnnotation.xls")
# head(annotation, 10)
```

#### what annatations provided, what are the names of the clinical information

## Data Processing

### Inspection on data missingness



## Quality Assessment


## Identify Protein Markers for Prognosis


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
