---
title: "DKFZ - SMART-CARE interview - coding task"
author: Siwen Chen
date: "`r Sys.Date()`"
theme: united
highlight: tango
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float:
      collapsed: true
      smooth_scroll: false
tags: protein_abundance
bibliography: references.bib  
---
# Packages used in this workflow 
Packages used are from @zhang2018proteome
```{r used_packages}
library(DEP)
library(stringr)
library(tidyr)
library(dplyr)
```

# Data Loading - Raw protein abundance data
```{r protein_abundance_data}
prot_abundance <- read.table(file = "Protein_abundance.tsv",
                              sep = "\t", header = TRUE)
head(prot_abundance, 2)
```

Give the dimension of the protein abundance data - containing 3942 proteins and 49 samples.
```{r}
dim(prot_abundance)
```

Check if there is any duplicated proteins - no duplicated protein.
```{r}
anyDuplicated(prot_abundance$X1)
```
Generate a SummerizedExperiment object for downstream analysis from the raw protein abundance data - As there is no replicate for each sample, the column names of the object ends with NA as shown in the warning message, which will not influence the downstrean analysis.
```{r}
# Transfer raw values into log2-transformed data - for better differential comparison
prot_abundance[, -1] <- log(prot_abundance[, -1], 2) + 1

# Sort the columns of the data frame numerically
prot_abundance <- prot_abundance[, c("X1", str_sort(colnames(prot_abundance[,-1]), numeric = TRUE))]
head(prot_abundance, 2)

# # Add suffix behind sampleIDs as replicate
# colnames(prot_abundance) <- c("X1", paste(colnames(prot_abundance[,-1]), "1", sep = "-"))
# head(prot_abundance, 2)

# Separate X1 column into proteinID and geneName
prot_abundance <- separate_wider_delim(prot_abundance, cols = X1, delim = "|", names = c("prefix", "protID", "geneName"))

# Prepare geneName and proteinID for the SummerizedExperiment object
prot_abundance <- make_unique(prot_abundance, "geneName", "protID")
head(prot_abundance, 2)

# Generate the SummerizedExperimen object
column_names <- grep("A_1_", colnames(prot_abundance))
SE <- make_se_parse(prot_abundance, column_names, mode = "delim", sep = "-")
SE
```

# Data Processing - Normalization and Missingness

Plot the number of proteins overlapped among samples - The barplot shows that most proteins can be identified in all samples, as indicated in the last bar.
```{r}
plot_frequency(SE)
```

## Data Missingness - Review on PBD slides to decide
On the other hand, there are still a high amount of proteins only existed in few samples, which contains many missing values and need to be imputed. 
```{r}
# Filter off proteins identified in more than 2/3 samples
SE_filtered_missingvals <- filter_proteins(SE, "fraction", min = 0.66)
plot_frequency(SE_filtered_missingvals)
```

Plot a barplot of the protein numbers among all samples, after removing the missing values.
```{r}
plot_numbers(SE_filtered_missingvals)
```

Plot a barplot of the protein numbers with different coverages among samples.
```{r}
plot_coverage(SE_filtered_missingvals)
```

## Data Normalization

Background corrected and normalized by variance stabilizing transformation 
```{r}
SE_norm <- normalize_vsn(SE_filtered_missingvals)
plot_normalization(SE_filtered_missingvals, SE_norm)

```

## annotation data
```{r annotation}
## Loading required package: readxl
# annotation <- read_excel("sampleAnnotation.xls")
# head(annotation, 10)
```

#### what annatations provided, what are the names of the clinical information



# Quality Assessment


# Identify Protein Markers for Prognosis


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
