---
title: "DKFZ - SMART-CARE interview - coding task"
author: Siwen Chen
date: "`r Sys.Date()`"
theme: united
highlight: tango
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float:
      collapsed: true
      smooth_scroll: false
tags: protein_abundance
bibliography: references.bib  
---
# Packages used 
Packages used are from @zhang2018proteome
```{r used_packages}
library(DEP)
library(stringr)
library(tidyr)
library(dplyr)
library(SummarizedExperiment)
library(readxl)
```
# Data Loading

# Load raw protein abundance data
```{r protein_abundance_data}
prot_abundance <- read.table(file = "Protein_abundance.tsv", sep = "\t", header = TRUE)

# Set the protein names as row index
rownames(prot_abundance) <- prot_abundance$X1
prot_abundance <- prot_abundance %>% select(starts_with("A_1_"))

# Sort the columns of the data frame numerically
prot_abundance <- prot_abundance[, str_sort(colnames(prot_abundance), numeric = TRUE)]

head(prot_abundance, 2)
```

## Load sample annotations
```{r}
## Loading required package: readxl
annotation <- read_excel("sampleAnnotation.xls")

# Remove the last sample as there is no protein abundance measurement provided
annotation <- annotation[-50, ]

# Convert data types
annotation$operator <- as.factor(annotation$operator)
annotation$batch <- as.factor(annotation$batch)
annotation[4] <- as.double(unlist(annotation[4]))
annotation$freeThawCycle <- as.factor(annotation$freeThawCycle)

# # Change names for DEP
# colnames(annotation) <- c("label", "operator", "condition", "total.protein.concentration", "replicate", "data.of.diagnosis", "died", "last.known.alive")

head(annotation, 2)
```

Create a SummerizedExperiment object containing both data
```{r}
# Prepare rowData for the SE object
rows <- data.frame(rownames(prot_abundance))
rows <- separate_wider_delim(rows, cols = rownames.prot_abundance., delim = "|", names = c("prefix", "protID", "geneName"))

se <- SummarizedExperiment(prot_abundance, colData=DataFrame(annotation), rowData=DataFrame(name=rows$geneName, ID=rows$protID))
se
```
The experiment contains 3942 proteins and 49 samples.

Check if there is any duplicated proteins - no duplicated protein.
```{r}
anyDuplicated(rownames(prot_abundance))
```

# Data Processing - Normalization and Missingness

Plot the number of proteins overlapped among samples - The barplot shows that most proteins can be identified in all samples, as indicated in the last bar.
```{r}
plot_frequency(se)
```

## Data Missingness - Review on PBD slides to decide
On the other hand, there are still a high amount of proteins only existed in few samples, which contains many missing values and need to be imputed. 
```{r}
# Filter off proteins identified in more than 2/3 samples
se_filtered_missingvals <- filter_proteins(se, "fraction", min = 0.66)
plot_frequency(se_filtered_missingvals)
```

Plot a barplot of the protein numbers among all samples, after removing the missing values.
```{r}
plot_numbers(se_filtered_missingvals)
```

Plot a barplot of the protein numbers with different coverages among samples.
```{r}
plot_coverage(se_filtered_missingvals)
```

## Data Normalization

Background corrected and normalized by variance stabilizing transformation 
```{r}
se_norm <- normalize_vsn(se_filtered_missingvals)
plot_normalization(se_filtered_missingvals, se_norm)

```

# Quality Assessment



# Identify Protein Markers for Prognosis






```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
